---
title: "Dot plot for mouse single-cell KPC from Elyada et al 2019"
author: Astrid Deschênes, Pascal Belleau and David A. Tuveson
output:
    BiocStyle::html_document:
        number_sections: no
        toc: true
    pkgdown:
        number_sections: no
        as_is: true
urlcolor: darkred
linkcolor: darkred
bibliography: mouseKPCscElyada2019shiny.bibtex
vignette: >
    %\VignetteIndexEntry{Dot plot for mouse single-cell KPC from Elyada et al 2019}
    %\VignettePackage{mouseKPCscElyada2019shiny}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
    library(knitr)
    library(mouseKPCscElyada2019shiny)
})

set.seed(121)
```

<br />

**Package**: `r Rpackage("mouseKPCscElyada2019shiny")`<br />
**Authors**: `r packageDescription("mouseKPCscElyada2019shiny")[["Author"]]`<br />
**Version**: `r packageDescription("mouseKPCscElyada2019shiny")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("mouseKPCscElyada2019shiny")[["License"]]`<br />




<br>
<br>



# Session info

Here is the output of `sessionInfo()` in the environment in which this 
document was compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<br>
<br>


# References
